Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-04-14 0_coverletter/itt-emotion-coverletter.tex
Edited V7-2 a bit in Intro and made cover letter

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further. This was a minor revision, with a few additions to the reviewed literature.

As stated before, We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels. We discuss theories on the reason behind this in our revised paper. We also found that Chinese tourists in Japan are interested in shopping at all price ranges of hotels, while Western tourists are more inclined to shop when staying in middle to high-priced hotels.

We believe this was an appropriate response to the minor revision, and hope we continue to be in your consideration.

>>>>

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem. Therefore, in this revision, we made a few changes to the structure of section "3. Theoretical background and hypothesis development", adding more literature we reviewed, and added to the Abstract, Introduction, and Research objective sections as well.

In the abstract, we added a concise background of why we are interested in a cross-culture study using a large data-base. In the introduction, we add citations to clarify the influence of culture on expectations, perceptions of quality and satisfaction, and the importance to analyze the difference between Chinese and Western tourists specifically in Japan (l.17-l.27, l.37-l.41). We also added on the necessity to do this analysis on a large scale with automatic methodologies (l.60-l.67). We also added to the research objective section to clarify the reasoning behind the objective (l.92-l.95).

In the Theoretical background section, we moved the section "3.1 Japanese hospitality and service: \textit{Omotenashi}" to 3.3, and talked about the theory behind satisfaction, expectations, and their relationship to culture in the new sections 3.1 and 3.2, which add content and citations to what previously was section "3.2 Customer satisfaction and dissatisfaction towards individual factors during hotel stay". It was split into two sections to avoid going off topic, since one of them explains the theory of expectations leading to satisfaction, while the other one explains the theory behind our approach to studying the customers' satisfaction. Lastly, we added a section "3.4 Customer expectations beyond service and hospitality" to explain the reasoning behind studying hard and soft attributes better.

We believe this was an appropriate response to the major revision, and hope we continue to be in your consideration.

### 2021-04-14 1_manuscript/itt-emotion.tex
Edited V7-2 a bit in Intro and made cover letter

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and
                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \and
                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}. Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations. This diversity means that the expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  Our study focuses on Western and Chinese tourists, considering their numbers. Chinese tourists accounted for 25.63\% of the tourist population. On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}. Despite this, many tourist-behavior analyses have been performed only involving Western subjects. As such, a knowledge gap existed until recent decades.

  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations, namely, the scale and sampling. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose. These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study. This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results. For this, we used a data-driven approach to our analysis.

>>>>

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
                    \hspace*{1em} ORCID: 0000-0002-6437-0866
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and 
                    \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \at 
                    \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}. Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different.

  The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations. This diversity means that the expectations when staying at a hotel will be varied. Cultural backgrounds have a decisive role in aspects of satisfaction and in the perceptions of quality \cite[][]{mattila1999role,winsted1997service}, or behavioral intentions \cite[][]{liu2001relationships}, such as the difference in Westerners and Asians in their willingness to pay more \cite[][]{LEVY2010319}. A difference in cultural background can also heavily influence customers' expectations, as well as their perceptions of quality, and the difference between these two is what expresses itself as satisfaction. This difference in expectations and perceptions of quality can be smaller or larger depending on the culture in reaction to the same service.

  For a growing industry with increasing cultural diversity, it is essential to identify the cross-culture expectations of customers in order to provide the appropriate services, cater to these expectations to ensure and increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  In 2017, Chinese tourists accounted for 25.63\% of the tourist population. On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon, \cite[][]{sun2017}. Despite this, many tourist-behavior analyses have been performed only involving Western subjects. Yet, it is known that Western and Asian customers are heavily differentiated\cite[][]{LEVY2010319}. As such, a knowledge gap existed until recent decades. Considering the numbers of inbound tourists in Japan and our team's language capabilities, our study focuses on Western and Chinese tourists.

  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations, namely, the scale and sampling. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose. These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study. This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.

  However, with ever-increasing customer populations, this is hard to accomplish without extensive studies of the customer base. There is a need for an automated method for identifying these expectations at a large scale. Our study intends to answer the need for such a methodology utilizing machine learning and natural language processing of large amounts of data. For this, we used a data-driven approach to our analysis, taking advantage of hotel review data. With this methodology, we explore the expectations and needs for the two most differing cultures currently interacting with the hospitality industry in Japan.
